---
title: "Diminishing Returns"
author: "Bob Horton"
date: "October 15, 2018"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Less is More (per unit)

Here we use an equation to estimate the price for each unit, in a diminishing returns situation where the total market is finite. Specifically, we model the returns (revenue) as a parameterized function of the number of units sold (x).

$$
x_{equiv} = \begin{cases}
 x & \text{if } K = 0 \\
 \frac{(1 - e^{-K x})}{K} & \text{otherwise}
\end{cases}
$$

where the parameter K controls how quickly the market is saturated.

```{r diminishing_returns, echo=FALSE}

ui <- shinyUI(fluidPage(

  titlePanel("Diminishing Returns"),

  sidebarLayout(

    sidebarPanel(
      selectInput("num_widgets", label = "Number of units:",
                  choices = c(10, 100, 1000, 10000), selected = 100),
      sliderInput("K", label = "diminishment rate (K):", min = -0.1, max = 0.1, value = 0.001, step = 0.001)
    ),

    mainPanel(
      plotOutput("rocPlot")
    )
  )
))

diminishing_return <- function(x, K){
  if (K==0)
    x
  else
    (1 - exp(-K*x))/K
}

# input <- list(num_widgets=100, A=100, K=0.001)

server <- function(input, output) {

  output$rocPlot <- renderPlot({

    num_widgets <- as.numeric(input$num_widgets)
    K <- as.numeric(input$K)  # rate at which price declines with increasing supply
    
    units_sold <- seq(1, num_widgets)  # seq(0, num_widgets)
    
    dret <- diminishing_return(units_sold, K)
    
    plot(units_sold, dret, type='b', 
         # xlim=c(0, num_widgets), ylim=c(0, num_widgets),
         xlab="units sold", ylab="cumulative revenue",
         main="Total revenue")

    abline(0, 1, lty=2, col="blue")

  }, width=600, height=600)
}

options <- list(width = 600, height = 1200)

shinyApp(ui, server,  options=options)

```


The blue line shows non-diminishing returns, where each unit sold adds a constant amount to revenue. The parameter `K` controls how quickly the returns diminish, and also the asymptotic ceiling for returns. Positive values of `K` lead to more rapid falloff in returns, so the black curve begins to droop below the blue reference line. Positive values of `K` cause the black curve to lift above the blue reference curve. When `K == 0` we have constant unit revenue (the equation is not defined at K==0, so we add a special case.)